%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
\cventry
    {Software Engineer} % Job title
    {Fwaygo} % Organization
    {Los Angeles, CA} % Location
    {Jun. 2021 - Sep. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Designed and developed distributed microservices in Go for
        user/song data processing, report handling, and server-to-client
        messaging.}
        \item {Leveraged Firebase and GraphQL to implement client-side metrics
        tracking, message receiving, and account management.}
        \item {Technologies: Go, GraphQL, RabbitMQ, Firebase, AWS, Typescript,
        React Native}
      \end{cvitems}
    }

\cventry
    {Software Developer} % Job title
    {NurLabs} % Organization
    {Los Angeles, CA} % Location
    {Apr. 2021 - Jun. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Collaborated with UCLA researchers to develop a script using Bash
        and Python for mass extracting data from Raman Spectroscopy .WDF output
        files to train a machine learning lung cancer detection model.}
        \item {Accelerated data extraction speed from 2 minutes per document to
        less than one second overall.}
        \item {Worked with UCLA Anderson students to implement a server for
        receiving and storing client data using PostgreSQL, Heroku, and Node.}
      \end{cvitems}
    }

\cventry
    {Software Developer} % Job title
    {WeChews} % Organization
    {Los Angeles, CA} % Location
    {Sep. 2020 - Apr. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Collaborated with a team of 10 students to build a React Native
        app that matches users with restaurants to eat at via a Tinder-like
        swiping flow.}
        \item {Implemented back-end image uploading and notification sending
        using AWS S3 and FCM integrated with PostgreSQL and Node/Express .}
      \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}
