%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
\cventry
    {Software Engineer} % Job title
    {Fwaygo} % Organization
    {Los Angeles, CA} % Location
    {Jun. 2021 - Sep. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Designed and developed server microservices in Go for user/song
        metrics and data processing and server-to-client messaging.}
        \item {Implemented client-side metrics tracking, message feed, and
        account management.}
        \item {Technologies: Go, GraphQL, RabbitMQ, Firebase, AWS, Typescript,
        React Native}
      \end{cvitems}
    }

\cventry
    {Software Developer} % Job title
    {NurLabs} % Organization
    {Los Angeles, CA} % Location
    {Apr. 2021 - Jun. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Collaborated with UCLA researchers to develop a script using Bash
        and Python for mass extracting data from Raman Spectroscopy .WDF output
        files to train a machine learning lung cancer detection model.}
        \item {Decreased data extraction process from over 30 minutes to under a
        second.}
      \end{cvitems}
    }

\cventry
    {Software Developer} % Job title
    {WeChews} % Organization
    {Los Angeles, CA} % Location
    {Sep. 2020 - Apr. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Collaborated with a team of 10 students to build a React Native
        app that matches users with restaurants to eat at via a Tinder-like
        swiping flow.}
        \item {Implemented back-end image uploading and notification sending
        using AWS S3 and FCM integrated with PostgreSQL and Node/Express .}
      \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}
