\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Software Engineer}{Apr. 2024 -- Present}
      {Meta}{New York, NY}
      \resumeItemListStart
        \resumeItem{Facebook Scam \& Trust; Tech lead for ML modeling/infrastructure for scam detection on FB Dating Integrity}
        \resumeItem{Owned end-to-end development and training of production scam detection models, spanning scam trend research, feature engineering, offline evaluation, and online inference; reduced scam view prevalence by 70\%}
        % \resumeItem{Own E2E development and training of scam detection models, driving collaboration across Eng, DS, and PMs to research scam trends and develop new features. Reduced scam view prevalence by 70\% with model improvements}
        \resumeItem{Re-architected model-serving infrastructure handling 150M+ daily users, introducing caching, batching, and rate limiting to cut direct inference volume by 98\%+, and reduce compute spend by \$200k/yr}
        \resumeItem{Led development of user-facing trust feature, coordinating across 18 cross-functional stakeholders. Achieved 20\% adoption in 30 days and scaled into a company-wide trust initiative}
        \resumeItem{Drove cross-team collaboration with 12 engineers to define and execute a multi-half roadmap to unify FB-wide integrity infrastructure, reducing system fragmentation and improving reliability and operational maintainability}
      \resumeItemListEnd

    \resumeSubheading
      {Software Engineer Intern}{Jun. 2023 -- Aug. 2023}
      {Citadel Securities}{New York, NY}
      \resumeItemListStart
        \resumeItem{Trading Ecosystem, focused on optimizing trading infrastructure performance}
        \resumeItem{Built distributed tracing services across order execution infrastructure to enable real-time error detection and correction, cutting investigation time from hours to seconds}
        \resumeItem{Developed an internal library for streaming Kafka data to q/kdb+, improving data throughput by 1.5x}
        \resumeItem{Built load-testing infrastructure to simulate 100k+ concurrent orders for trade booking system to benchmark latency and failure modes under stress}
      \resumeItemListEnd

    \resumeSubheading
      {Software Engineer Intern}{Jun. 2022 -- Sep. 2022}
      {Meta}{Menlo Park, CA}
      \resumeItemListStart
        \resumeItem{Instagram Demand \& Efficiency Management, focused on improving Instagram's backend power efficiency}
        \resumeItem{Led cross-team project to develop a system measuring engagement change per kilowatt used for proposed features}
        \resumeItem{Built power monitoring dashboard covering 25 services and 500K+ servers, centralizing visibility for energy usage}
        \resumeItem{Developed algorithm to triage power regressions to launches by correlating launch data with power time-series data}
      \resumeItemListEnd

    \resumeSubheading
      {Software Engineer Intern}{Jun. 2021 -- Sep. 2021}
      {Fwaygo}{Los Angeles, CA}
      \resumeItemListStart
        \resumeItem{Developed microservices in Go for user/song data processing, report handling, and server‐to‐client messaging}
        \resumeItem{Utilized RabbitMQ to facilitate interservice pub/sub communication between Docker container clusters on GKE}
        \resumeItem{Created GraphQL APIs for user/song queries \& mutations and integrated them into a React Native frontend}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    % \resumeSubheading
    %   {Software Developer}{Apr. 2021 -- Jun. 2021}
    %   {NurLabs}{Los Angeles, CA}
    %   \resumeItemListStart

    %     \resumeItem{Collaborated with UCLA researchers on using machine learning to detect lung cancer from spectroscopy data}
    %     \resumeItem{Developed a script to batch extract spectroscopy data from .WDF files, accelerating data extraction from 2 minutes per file to under 1 second overall}
    %     \resumeItem{Created a server and API for receiving and storing client information using PostgreSQL, Node, and Express}
    %     % REGINA: Remove next line 
    %     % \resumeItem{Practiced agile scrum methodology through daily stand-ups with founders from UCLA Anderson} 
    %   \resumeItemListEnd

    % \resumeSubheading
    %   {Full Stack Developer}{Sep. 2020 -- Apr. 2021}
    %   {WeChews}{Los Angeles, CA}
    %   \resumeItemListStart
    %     \resumeItem{Collaborated with a team of 10 to build a React Native app that matches users with restaurants to eat at}
    %     \resumeItem{Implemented push notification service with Google Cloud Messaging and image uploading with Amazon S3}
    %     \resumeItem{Developed a REST API for notifications using PostgreSQL, Node, and Express}
    %   \resumeItemListEnd

  \resumeSubHeadingListEnd